---
title: "Forecasting the CO2 Time Series with Meta Prophet" 
subtitle: "Coursework 1" 
author: "Shante Constable" 
date: "Spring term 2025" 
output: 
  html_document:
    toc: true
    toc_float: true
    theme: spacelab 
    highlight: tango
---
 
```{r, echo=FALSE}
# This code will display the QMUL logo at the top right of the page
# Do not change this code
htmltools::img(src = knitr::image_uri("images/QMlogo.png"),
               alt = 'logo',
               style = 'position:absolute; top:0; right:0; padding:10px; width:20%;')
```

## Libraries

```{r}
library(prophet)
library(zoo)
```


# Introduction 

This project uses the data in Meta Prohpet to study and forecast,in R, the built-in C02 time series.

## Data

```{r}
co2_dataframe = data.frame(
 ds = as.Date(as.yearmon(time(co2))),
 y = as.numeric(co2)
)

head(co2_dataframe)
```
The co2 data is a time series, taken monthly so i converted it into ds and y becasue of Prophet. 
## Prophet model

```{r}
co2_prophet_model = prophet(co2_dataframe)
future_co2_dates = make_future_dataframe(co2_prophet_model, periods = 24, freq = "month")
co2_forecast = predict(co2_prophet_model, future_co2_dates)
plot(co2_prophet_model, co2_forecast)
```
Here I created a Prophet model, made dates for the future and predicted the next 24 months.

## Comment 
The forecast continues the overall upward trend in the time series.
There is also a repeating seasonal pattern acroos the years. 
So Prophet has obtained both long-term and seasonal patterns. 


